FictionEro - Data Cleaning

### 2024-02-15 analysis/1_cleaning.qmd
update cleaning #9

# Table
summarize(df, N = n(), .by=c("Language", "Experimenter")) |> 
  arrange(desc(N)) |> 
  gt::gt() |> 
  gt::opt_stylize() |> 
  gt::opt_interactive(use_compact_mode = TRUE) 
```

@@

@@

@@

outliers <- c(
  # "S344"  # Negative Arousal-Valence correlations
  )
potentials <- list()
```

@@

```{r}
plot_hist <- function(dat) {
  dat |> 
    mutate(Participant = fct_reorder(Participant, RT1)) |> 
    filter(RT1 < 100) |> 
    ggplot(aes(x=RT1, fill=Participant)) +
    geom_histogram(bins=140) +
    coord_cartesian(xlim = c(0, 15)) +
    scale_fill_metro_d(guide="none") +
    theme_modern() +
    theme(axis.title.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.text.y = element_blank(),
          axis.line.y = element_blank()) +
    labs(title = "Distribution of Response Time for each Participant", x="Response time (for 3 scales) per stimuli (s)") +
    facet_wrap(~Participant, ncol=5, scales="free_y")
}
```

@@

@@

df |>
  mutate(Participant = fct_reorder(Participant, BAIT_Duration),
         Category = ifelse(BAIT_Duration > 5, "extra", "ok"),
         Duration = ifelse(BAIT_Duration > 5, 5, BAIT_Duration),
         Group = ifelse(Participant %in% outliers, "Outlier", "ok")) |>
  ggplot(aes(y = Participant, x = Duration)) +
  geom_point(aes(color = Group, shape = Category)) +
  geom_vline(xintercept = median(df$BAIT_Duration), color = "red", linetype = "dashed") +
  scale_shape_manual(values = c("extra" = 3, ok = 19)) +
  scale_color_manual(values = c("Outlier" = "red", ok = "black"), guide="none") +
  guides(color = "none", shape = "none") +
  ggside::geom_xsidedensity(fill = "#9C27B0", color=NA) +
  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
  labs(
    title = "Questionnaire Completion Time",
    x = "Duration (in minutes)",
    y = "Participant"
  )  +
  theme_bw() +
  ggside::theme_ggside_void() +
  theme(ggside.panel.scale = .3,
        panel.border = element_blank()) 
```

@@

show_distribution <- function(dftask, target="Arousal") {
  dftask |> 
    filter(SexualOrientation %in% c("Heterosexual", "Bisexual", "Homosexual")) |>
    bayestestR::estimate_density(select=target, 
                                 at=c("Relevance", "Category", "Sex", "SexualOrientation"), 
                                 method="KernSmooth") |>
    ggplot(aes(x = x, y = y)) +
    geom_line(aes(color = Relevance, linetype = Category)) +
    facet_grid(SexualOrientation~Sex, scales="free_y")  +
    scale_color_manual(values = c("Relevant" = "red", "Non-erotic" = "blue", "Irrelevant"="orange")) +
    scale_y_continuous(expand = c(0, 0)) +
    scale_x_continuous(expand = c(0, 0)) +
    theme_minimal()  +
    theme(axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          plot.title = element_text(face="bold")) +
    labs(title = target) 
}

@@

```{r p_demographics_sex}
colors <- c(
  "NA" = "#2196F3", "No" = "#E91E63", "Condoms (for partner)" = "#9C27B0",
  "Combined pills" = "#FF9800", "Intrauterine Device (IUD)" = "#FF5722", 
  "Intrauterine System (IUS)" = "#795548"
)
colors <- colors[names(colors) %in% c("NA", df$BirthControl)]

@@

@@

marginaleffects::predictions(m, by=c("AI_Knowledge"), newdata = "marginalmeans") |> 
  as.data.frame() |> 
  ggplot(aes(x=AI_Knowledge, y=estimate)) +
  geom_jitter2(data=df, aes(y=BAIT_SEM), alpha=0.2, width=0.1) +
  geom_line(aes(group=1), position = position_dodge(width=0.2)) +
  geom_pointrange(aes(ymin = conf.low, ymax=conf.high), position = position_dodge(width=0.2))
```

>>>>

# Table
summarize(df, N = n(), .by=c("Language", "Experimenter")) |> 
  arrange(desc(N)) |> 
  gt::gt() |> 
  gt::opt_stylize() |> 
  gt::opt_interactive(use_compact_mode = TRUE) |> 
  gt::tab_header("Number of participants per recruitment source")
```

@@

The majority of participants found it to be a "fun" experience. It is interesting to note that reports of "fun" were significantly associated with finding (some) stimuli arousing. Conversely, reporting "no feelings" was associated with finding the experiment "boring".

#### Proportion

@@

#### Co-occurence

```{r}
cor <- df |> 
  select(starts_with("Feedback"), -Feedback_Comments) |> 
  mutate_all(~ifelse(.=="True", 1, 0)) |> 
  correlation(method="tetrachoric", redundant = TRUE) |> 
  correlation::cor_sort() |> 
  correlation::cor_lower()

cor |> 
  mutate(val = paste0(insight::format_value(rho), format_p(p, stars_only=TRUE))) |>
  mutate(Parameter2 = fct_rev(Parameter2)) |>
  mutate(Parameter1 = fct_relabel(Parameter1, \(x) str_remove_all(x, "Feedback_")),
         Parameter2 = fct_relabel(Parameter2, \(x) str_remove_all(x, "Feedback_"))) |>
  ggplot(aes(x=Parameter1, y=Parameter2)) +
  geom_tile(aes(fill = rho), color = "white") +
  geom_text(aes(label = val), size = 3) +
  labs(title = "Feedback Co-occurence Matrix") +
  scale_fill_gradient2(
    low = "#2196F3",
    mid = "white",
    high = "#F44336",
    breaks = c(-1, 0, 1),
    guide = guide_colourbar(ticks=FALSE),
    midpoint = 0,
    na.value = "grey85",
    limit = c(-1, 1))  + 
  theme_minimal() +
  theme(legend.title = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1))
```

@@

outliers <- c(
  # "S206"  # Collapsed RTs in both phases
  # "S399"  # Negative Arousal-Valence correlations
  )
potentials <- list()
```

@@

```{r}
plot_hist <- function(dat) {
  dens <- rbind(
    mutate(bayestestR::estimate_density(filter(dftask, RT1 < 40 & RT2 < 40)$RT1), 
           Phase="Emotional ratings",
           y = y / max(y)),
    mutate(bayestestR::estimate_density(filter(dftask, RT1 < 40 & RT2 < 40)$RT2), 
           Phase="Reality rating",
           y = y / max(y))
  )

  dat |> 
    filter(RT1 < 40 & RT2 < 40) |>  # Remove very long RTs
    # mutate(Participant = fct_reorder(Participant, RT1)) |> 
    pivot_longer(cols = c(RT1, RT2), names_to = "Phase", values_to = "RT") |>
    mutate(Phase = ifelse(Phase == "RT1", "Emotional ratings", "Reality rating")) |>
    ggplot(aes(x=RT)) +
    geom_area(data=dens, aes(x=x, y=y, fill=Phase), alpha=0.33, position="identity") +
    geom_density(aes(color=Phase, y=after_stat(scaled)), linewidth=1.5) + 
    scale_x_sqrt(breaks=c(0, 2, 5, 10, 20)) +
    theme_minimal() +
    theme(axis.title.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.text.y = element_blank(),
          axis.line.y = element_blank()) +
    labs(title = "Distribution of Response Time for each Participant", x="Response time per stimuli (s)") +
    facet_wrap(~Participant, ncol=5, scales="free_y") +
    coord_cartesian(xlim = c(0, 25))
}
```

@@

#### 181-240

plot_hist(dftask[dftask$Participant %in% df$Participant[181:240], ])
```

#### 241-300

plot_hist(dftask[dftask$Participant %in% df$Participant[241:264], ])
```

@@

df |>
  mutate(Participant = fct_reorder(Participant, BAIT_Duration),
         Category = ifelse(BAIT_Duration > 5, "extra", "ok"),
         Duration = ifelse(BAIT_Duration > 5, 5, BAIT_Duration),
         Group = ifelse(Participant %in% outliers, "Outlier", "ok")) |>
  ggplot(aes(y = Participant, x = Duration)) +
  geom_point(aes(color = Group, shape = Category)) +
  geom_vline(xintercept = median(df$BAIT_Duration), color = "red", linetype = "dashed") +
  scale_shape_manual(values = c("extra" = 3, ok = 19)) +
  scale_color_manual(values = c("Outlier" = "red", ok = "black"), guide="none") +
  guides(color = "none", shape = "none") +
  ggside::geom_xsidedensity(fill = "#9C27B0", color=NA) +
  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
  labs(
    title = "Questionnaire Completion Time",
    x = "Duration (in minutes)",
    y = "Participant"
  )  +
  theme_bw() +
  ggside::theme_ggside_void() +
  theme(ggside.panel.scale = .3,
        panel.border = element_blank(),
        axis.ticks.y = element_blank(),
          axis.text.y = element_blank()) 
```

@@

show_distribution <- function(dftask, target="Arousal") {
  dftask |> 
    filter(SexualOrientation %in% c("Heterosexual", "Bisexual", "Homosexual")) |>
    bayestestR::estimate_density(select=target, 
                                 at=c("Relevance", "Category", "Sex", "SexualOrientation"), 
                                 method="KernSmooth") |>
    ggplot(aes(x = x, y = y)) +
    geom_line(aes(color = Relevance, linetype = Category), linewidth=1) +
    facet_grid(SexualOrientation~Sex, scales="free_y")  +
    scale_color_manual(values = c("Relevant" = "red", "Non-erotic" = "blue", "Irrelevant"="darkorange")) +
    scale_y_continuous(expand = c(0, 0)) +
    scale_x_continuous(expand = c(0, 0)) +
    theme_minimal()  +
    theme(axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          plot.title = element_text(face="bold")) +
    labs(title = target) 
}

@@

```{r p_demographics_sex}
colors <- c(
  "NA" = "#2196F3", "None" = "#E91E63", "Condoms (for partner)" = "#9C27B0",
  "Combined pills" = "#FF9800", "Intrauterine Device (IUD)" = "#FF5722", 
  "Intrauterine System (IUS)" = "#795548", "Progestogen pills" = "#4CAF50",
  "Other" = "#FFC107", "Condoms (female)" = "#607D8B"
)
colors <- colors[names(colors) %in% c("NA", df$BirthControl)]

@@

While the two correlate substantially, they have different benefits. The empirical score has a more straightforward meaning and is more reproducible (as it is not based on a model fitted on a specific sample), the model-based score takes into account the relative importance of the contribution of each item to their factor.

@@

marginaleffects::predictions(m, by=c("AI_Knowledge"), newdata = "marginalmeans") |> 
  as.data.frame() |> 
  ggplot(aes(x=AI_Knowledge, y=estimate)) +
  geom_jitter2(data=df, aes(y=BAIT_SEM), alpha=0.2, width=0.1) +
  geom_line(aes(group=1), position = position_dodge(width=0.2)) +
  geom_pointrange(aes(ymin = conf.low, ymax=conf.high), position = position_dodge(width=0.2)) +
  theme_minimal() +
  labs(x = "AI-Knowledge", y="BAIT Score")
```
